\huge{Comment on `The Limits of Cosmic Shear'}

### 2016-12-02 cfhtlens.tex
Now with section 3.1 on the comparison of xi, map and COSEBIS

Our findings are in disagreement with \citet{kitching/etal:2016} who find a shift of $\Delta \sigma_8 = 0.007$ between their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) and their `Limber' analysis (which we believe corresponds to 
the Extended Limber spherical case in Table~\ref{tab:Tl_nu}).

\subsection{Comparison of two-point shear statistics; the two-point correlation function, mass aperture statistic and COSEBIS}
\citet{kilbinger/etal:2013} present the most detailed comparison to date of constraints from a range different two-point shear statistics.

>>>>

Our Limber-case findings are therefore in disagreement with \citet{kitching/etal:2016} who find a shift of $\Delta \sigma_8 = 0.007$ between their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) and their `Limber' analysis (which we believe corresponds to the Extended Limber spherical case in Table~\ref{tab:Tl_nu}).

\subsection{Comparison of two-point shear statistics; the two-point correlation function, mass aperture statistic and COSEBIS}
\citet{kilbinger/etal:2013} present a detailed comparison of cosmological constraints obtained from a range different two-point shear statistics including the shear correlation function, $\xi_\pm$, the mass aperture statistic, $M_ {\rm ap}^2$ \citep{schneider/etal:1998}, and the COSEBIs statistics \citep{schneider/etal:2010}.  As shown by each statistic's weight function in figure~\ref{fig:filters}, these two-point cosmic shear statistics exhibit different dependences between the angular scales sampled and the $\ell$-range probed.   If a significant bias had been introduced at low-$\ell$ by using flat-sky and Limber approximations, we would then expect to see a systematic shift between the different two-point statistics with the COSEBI statistic being completely unaffected as it only includes modes with $\ell \gtrsim 80$.  This is found not to be the case with all three statistics finding $\sigma_8 (\Omega_m/0.27)^\alpha = 0.79$ with errors than range from $0.03$ to $0.06$ \citep[see Table 5 of][]{kilbinger/etal:2013}.  This comparison further supports our argument that the approximations highlighted by \citet{kitching/etal:2016} have negligible impact for current surveys.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.5\textwidth]{figures/ellWnPell1-100.pdf}
\caption{ \label{fig:filters}.  Currently just COSEBIS, will also have $\xi_\pm$ and $M_{\rm ap}^2$.}
\end{center}
\end{figure}

### 2016-12-02 conclusion.tex
Now with section 3.1 on the comparison of xi, map and COSEBIS

In this comment we have highlighted a number of shortcomings in the analysis presented in \cite{kitching/etal:2016}.  We argue that the flat sky and Limber approximations that can be used in cosmic shear analyses are not able to explain away the tension between current weak lensing and Planck results, in contrast to the message that \cite{kitching/etal:2016} convey.  Our critique should not, however, detract from the extremely important core message of their paper, that future surveys will need to carefully consider these approximations and optimise their statistical analyses accordingly.  For example moving from the standard two-point shear correlation function statistic to the more stringent `COSEBI' statistic renders the cosmic shear measurement completely insensitive to the low-$\ell$ scales where these approximations become important \citep{schneider/etal:2010}.

>>>>

In this comment we have highlighted a number of shortcomings in the analysis presented in \cite{kitching/etal:2016}.  We argue that the flat sky and Limber approximations that can be used in cosmic shear analyses are not able to explain away the tension between current weak lensing and Planck results, in contrast to the message that \cite{kitching/etal:2016} convey.  Our critique should not, however, detract from the important core message of their paper, that future surveys will need to consider these approximations and optimise their statistical analyses accordingly.  For example moving from the standard two-point shear correlation function statistic to the more stringent `COSEBI' statistic \citep{schneider/etal:2010} renders the cosmic shear measurement completely insensitive to the low-$\ell$ scales where these approximations become important.
